Towards Practical First-Order Model Counting

### 2025-06-14 doc/talk/functions.tex
Better plots

% Created by tikzDevice version 0.12.6 on 2025-06-13 10:38:23
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\setlength\PreviewBorder{0pt}
\begin{document}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,201.36) -- ( 35.24,201.36);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (307.15,216.81);
\definecolor{drawColor}{gray}{0.30}

>>>>

% Created by tikzDevice version 0.12.6 on 2025-06-14 12:29:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\setlength\PreviewBorder{0pt}

\usepackage{siunitx}
\usepackage{siunitx}
\sisetup{group-separator = {,}}\begin{document}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] ( 29.55,201.36) -- ( 35.24,201.36);
\definecolor{drawColor}{RGB}{169,169,169}

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 4pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (101.55,198.27) -- (290.23,198.27);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (117.19,207.30) --
	(101.55,198.27) --
	(117.19,189.23);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] (274.59,189.23) --
	(290.23,198.27) --
	(274.59,207.30);
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
	(225.43,191.14) --
	(225.35,191.14) --
	(225.67,191.16) --
	(225.99,191.22) --
	(226.29,191.33) --
	(226.57,191.49) --
	(226.81,191.70) --
	(227.03,191.94) --
	(227.20,192.21) --
	(227.32,192.50) --
	(227.40,192.82) --
	(227.43,193.14) --
	(227.43,193.14) --
	(227.43,203.40) --
	(227.43,203.40) --
	(227.40,203.72) --
	(227.32,204.03) --
	(227.20,204.33) --
	(227.03,204.60) --
	(226.81,204.84) --
	(226.57,205.04) --
	(226.29,205.20) --
	(225.99,205.32) --
	(225.67,205.38) --
	(225.43,205.39) --
	(166.35,205.39) --
	(166.59,205.38) --
	(166.27,205.39) --
	(165.95,205.35) --
	(165.64,205.26) --
	(165.35,205.13) --
	(165.08,204.94) --
	(164.85,204.72) --
	(164.66,204.47) --
	(164.51,204.18) --
	(164.41,203.88) --
	(164.36,203.56) --
	(164.35,203.40) --
	(164.35,193.14) --
	(164.36,193.30) --
	(164.36,192.98) --
	(164.41,192.66) --
	(164.51,192.35) --
	(164.66,192.07) --
	(164.85,191.81) --
	(165.08,191.59) --
	(165.35,191.41) --
	(165.64,191.27) --
	(165.95,191.18) --
	(166.27,191.14) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.10] at (195.89,194.47) {$> \num{500000} \times$};
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
\definecolor{fillColor}{RGB}{255,255,255}

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round,fill=fillColor] (166.35,191.14) --
	(225.43,191.14) --
	(225.35,191.14) --
	(225.67,191.16) --
	(225.99,191.22) --
	(226.29,191.33) --
	(226.57,191.49) --
	(226.81,191.70) --
	(227.03,191.94) --
	(227.20,192.21) --
	(227.32,192.50) --
	(227.40,192.82) --
	(227.43,193.14) --
	(227.43,193.14) --
	(227.43,203.40) --
	(227.43,203.40) --
	(227.40,203.72) --
	(227.32,204.03) --
	(227.20,204.33) --
	(227.03,204.60) --
	(226.81,204.84) --
	(226.57,205.04) --
	(226.29,205.20) --
	(225.99,205.32) --
	(225.67,205.38) --
	(225.43,205.39) --
	(166.35,205.39) --
	(166.59,205.38) --
	(166.27,205.39) --
	(165.95,205.35) --
	(165.64,205.26) --
	(165.35,205.13) --
	(165.08,204.94) --
	(164.85,204.72) --
	(164.66,204.47) --
	(164.51,204.18) --
	(164.41,203.88) --
	(164.36,203.56) --
	(164.35,203.40) --
	(164.35,193.14) --
	(164.36,193.30) --
	(164.36,192.98) --
	(164.41,192.66) --
	(164.51,192.35) --
	(164.66,192.07) --
	(164.85,191.81) --
	(165.08,191.59) --
	(165.35,191.41) --
	(165.64,191.27) --
	(165.95,191.18) --
	(166.27,191.14) --
	cycle;
\end{scope}
\begin{scope}
\path[clip] ( 29.55, 57.56) rectangle (302.65,212.31);
\definecolor{drawColor}{RGB}{169,169,169}
